---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hmmr

<!-- badges: start -->
<!-- badges: end -->

The goal of hmmr is to provide the heightmap meshing facility of the [hmm library](https://github.com/fogleman/hmm) to R. 

It currently does not do anything, the meshing is run but nothing is returned but an empty list and a message. 

TODO

- allow input from in memory matrix
- capture output triangles

```{r hmmr}
library(hmmr)
f <- system.file("extdata/volcano1.png", package = "hmmr", mustWork = TRUE)

hmmr:::hmm_triangles(f)


hmmr:::hmm_triangles(f, max_triangles = 50)

```
## notes

```
## https://github.com/fogleman/hmm
fs::dir_copy("../hmm/src", "./src")

tools::package_native_routine_registration_skeleton("../hmmr", "src/init.c",character_only = FALSE)
```

---
 Please note that the 'hmmr' project is released with a
  [Contributor Code of Conduct](https://github.com/hypertidy/hmmr/blob/master/CODE_OF_CONDUCT.md).
  By contributing to this project, you agree to abide by its terms.
  
