---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# meshr

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/hypertidy/meshr.svg?branch=master)](https://travis-ci.org/hypertidy/meshr)
<!-- badges: end -->

The goal of meshr is to provide the heightmap meshing facility of the [hmm library](https://github.com/fogleman/hmm) to R. 

It currently returns a matrix of XYZ coordinates - every three rows is a triangle. We can also set `file_stl` to write to STL if needed. 

WARNING: the orientation of the input and output is not assured at the moment and will change. 

TODO

- DONE: STL output
- DONE: allow input from in memory matrix
- DONE (see below): maintain mapping for geospatial coordinates
- DONE auto-rescale input to full greyscale range
- DONE capture output triangles
- maintain real world z values
- sort out use of hmm, see notes below and in 00_meshr.cpp
- support Windows
- support MacOS


## Installation

Only on Linux. 

```
sudo apt-get install libglm-dev
```

```R
remotes::install_github("hypertidy/meshr")
```

## Example


```{r meshr}
library(meshr)
#f <- system.file("extdata/volcano1.png", package = "meshr", mustWork = TRUE)

m <- meshr::hmm_triangles(volcano)


m50 <- meshr::hmm_triangles(volcano, max_triangles = 50)

```

Compare different numbers of triangles from volcano. 

```{r triangles}
plot(m50, type = "n", asp = 1)
ii <- rbind(matrix(seq_len(nrow(m50)), nrow = 3), NA)
polygon(m50[ii, ])


m500 <- meshr::hmm_triangles(volcano, max_triangles = 500)

plot(m500, type = "n", asp = 1)
ii <- rbind(matrix(seq_len(nrow(m500)), nrow = 3), NA)
polygon(m500[ii, ])

```

Now write to STL if needed  [check it out](https://github.com/hypertidy/meshr/blob/master/man/figures/volcano1.stl). 



```{r STL, eval=FALSE}
meshr::hmm_triangles(volcano, z_exaggeration = 30, stl_file = "man/figures/volcano2.stl")
```
## notes

```
## https://github.com/fogleman/hmm
f <- fs::dir_ls("../hmm/src")
fs::file_copy(f, "./src/", overwrite = TRUE)
fs::file_copy("../hmm/LICENSE.md", "src/")
tools::package_native_routine_registration_skeleton("../meshr", "src/init.c",character_only = FALSE)


```

```{r testing-example, eval=FALSE}
## local testing
library(raster)
d <- raadtools::readtopo("etopo2", xylim = raster::extent(100, 180, -70, -30))
d <- aggregate(d, fact = 8)

unlink("stl.stl"); meshr:::hmm_triangles(as.matrix(d),  stl_file = "stl.stl", invert = T)
rgl::rgl.clear(); r <- rgl::readSTL("stl.stl", plot = TRUE, col = "grey", lit = TRUE); rgl::aspect3d(1, 1, .2); rgl::rglwidget()
```

![alt text][topo]



## Example of restoring geospatial information. 

```{r geospatial, eval= FALSE}
library(ceramic)
ex <- raster::extent(144, 149, -44, -40)
el <- cc_elevation(ex, zoom = 5)
el[el < 1] <- NA
tris <- meshr:::hmm_triangles(as.matrix(el),   z_scale = TRUE)

## now re-map geographic coordinates back int
library(raster)
cell <- cellFromXY(setExtent(el, raster::extent(1, ncol(el), 1, nrow(el))), 
                   tris[,1:2] + 1)


tris[,1:2] <- xyFromCell(el, cell)

## and unproject just for fun
tris[,1:2] <- rgdal::project(tris[,1:2], projection(el), inv = TRUE)
rgl::rgl.clear(); rgl::triangles3d(tris[,1], tris[,2], tris[,3], 
                                   col = rep(c("white", "grey", "black", "darkgrey"), each = 3));
rgl::aspect3d(1, 1, .035); rgl::rglwidget()
rgl::par3d()$bbox


```

![alt text][geo_triangles]



---
 Please note that the 'meshr' project is released with a
  [Contributor Code of Conduct](https://github.com/hypertidy/meshr/blob/master/CODE_OF_CONDUCT.md).
  By contributing to this project, you agree to abide by its terms.
  



[topo]: man/figures/topo.png "Etopo2 / 8 as 77053 triangles in 38861 points"
[geo_triangles]: man/figures/geo_triangles.png "Tasmania triangulated in longlat"
