---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hmmr

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/hypertidy/hmmr.svg?branch=master)](https://travis-ci.org/hypertidy/hmmr)
<!-- badges: end -->

The goal of hmmr is to provide the heightmap meshing facility of the [hmm library](https://github.com/fogleman/hmm) to R. 

It currently does not do anything *unless `file_stl` is specified*, the meshing is run but nothing is returned but an empty list and a message. 

TODO

- DONE: STL output
- allow input from in memory matrix, and maintain real world z values
- capture output triangles
- sort out use of hmm, see notes below and in 00_hmmr.cpp
- DONE (see below): maintain mapping for geospatial coordinates

## Installation

Only on Linux. 

```
sudo apt-get install libglm-dev
```

```R
remotes::install_github("hypertidy/hmmr")
```

## Example


```{r hmmr}
library(hmmr)
f <- system.file("extdata/volcano1.png", package = "hmmr", mustWork = TRUE)

hmmr:::hmm_triangles(f)


hmmr:::hmm_triangles(f, max_triangles = 50)

```
## notes

```
## https://github.com/fogleman/hmm
fs::dir_copy("../hmm/src", "./src")

tools::package_native_routine_registration_skeleton("../hmmr", "src/init.c",character_only = FALSE)


```

```{r testing-example, eval=FALSE}
## local testing
library(raster)
d <- raadtools::readtopo("etopo2", xylim = raster::extent(100, 180, -70, -30))
d <- d - cellStats(d, min)
d <- d / (cellStats(d, max)/256)
d <- aggregate(d, fact = 8)
rgdal::writeGDAL(as(d, "SpatialGridDataFrame"), "etopo.png", drivername = "PNG")
unlink("stl.stl"); hmmr:::hmm_triangles("etopo.png",  stl_file = "stl.stl")
rgl::rgl.clear(); r <- rgl::readSTL("stl.stl", plot = TRUE, col = "grey", lit = TRUE); rgl::aspect3d(1, 1, .2); rgl::rglwidget()
```

![alt text][topo]



## Example of restoring geospatial information. 

```{r geospatial, eval= FALSE}
library(ceramic)
ex <- raster::extent(144, 149, -44, -40)
el <- cc_elevation(ex, zoom = 5)
el[el < 1] <- NA

el <- el - cellStats(el, min)
el <- el / (cellStats(el, max)/256)

tfile <- tempfile(fileext = ".png")
rgdal::writeGDAL(as(el, "SpatialGridDataFrame"), tfile, drivername = "PNG")
sfile <- tempfile(fileext = ".stl")
hmmr:::hmm_triangles(tfile,  stl_file = sfile, z_scale = TRUE)
tris <- rgl::readSTL(sfile, plot = FALSE)

## now re-map geographic coordinates back int
library(raster)
cell <- cellFromXY(setExtent(el, raster::extent(1, ncol(el), 1, nrow(el))), 
                   tris[,1:2] + 1)


tris[,1:2] <- xyFromCell(el, cell)

## and unproject just for fun
tris[,1:2] <- rgdal::project(tris[,1:2], projection(el), inv = TRUE)
rgl::rgl.clear(); rgl::triangles3d(tris[,1], tris[,2], tris[,3], 
                                   col = rep(c("white", "grey", "black", "darkgrey"), each = 3));
rgl::aspect3d(1, 1, .035); rgl::rglwidget()
rgl::par3d()$bbox


```

![alt text][geo_triangles]



---
 Please note that the 'hmmr' project is released with a
  [Contributor Code of Conduct](https://github.com/hypertidy/hmmr/blob/master/CODE_OF_CONDUCT.md).
  By contributing to this project, you agree to abide by its terms.
  



[topo]: man/figures/topo.png "Etopo2 / 8 as 77053 triangles in 38861 points"
[geo_triangles]: man/figures/geo_triangles.png "Tasmania triangulated in longlat"
